Running Anpan

### 2023-03-29 other/anpan.qmd
add anpan for pathways

```fish
echo -e "sample\tfeature\tabundance" > data/bwexlerae_genefamilies.tsv
for s in (cat has_bwex.txt)
    fd "$s"_genefamilies /grace/sequencing/processed/mgx/humann/main/ -x rg s__Blautia_wexlerae | sd '^q' "$s\t" >> data/bwexlerae_genefamilies.tsv
end

@@

and then added a header manually.

@@

>>>>

```fish
echo -e "sample\tfeature\tabundance" > data/bwexlerae_genefamilies.tsv
for s in (cat has_bwex.txt)
    fd "$s"_genefamilies /grace/sequencing/processed/mgx/humann/main/ -x rg s__Blautia_wexlerae | sd '^' "$s\t" >> data/bwexlerae_genefamilies.tsv
end

@@

@@

### Using Pathways

```fish
echo -e "sample\tfeature\tabundance" > data/bwexlerae_pathabundance.tsv
for s in (cat has_bwex.txt)
    fd "$s"_pathabundance /grace/sequencing/processed/mgx/humann/main/ -x rg s__Blautia_wexlerae | sd '^' "$s\t" >> data/bwexlerae_pathabundance.tsv
end

sd '^.+\t(.+\t.+\t.+)$' '$1' data/bwexlerae_pathabundance.tsv
sd '^FG\d+_S\d+\t$' '' data/bwexlerae_pathabundance.tsv
sd ', ' ' ' data/bwexlerae_pathabundance.tsv
```

df <- fread("data/bwexlerae_pathabundance.tsv")
df2 <- dcast(df[, .(feature, sample, abundance)],
                 feature ~ sample,
                 value.var = "abundance",
                 fun.aggregate = sum)
names(df2)[1] = "# Gene Family"
fwrite(df2, "data/bwexlerae_pathabundance_wide.tsv")
```

```{r}
bwex_results <- anpan(#bug_dir           = "/grace/sequencing/processed/mgx/humann/main",
                        bug_file          = "./data/bwexlerae_pathabundance_wide.tsv",
                        meta_file         = "./data/manuscript_meta.csv",
                        out_dir           = "./data/anpan",
                        # annotation_file   = "/path/to/annotation.tsv", #optional, used for plots
                        filtering_method  = "kmeans",
                        model_type        = "fastglm",
                        covariates        = c("ageMonths", "sex", "education"),
                        outcome           = "cogScore",
                        plot_ext          = "pdf",
                        save_filter_stats = TRUE)
```

```{r}
input_path = file.path("data", "anpan", "filter_stats",
                       "filtered_bwexlerae_pathabundance_wide.tsv.gz")
